NOSQL INSIDE SQL

### 2018-02-18 pgconfus2018/presentation.tex
Basis for pgconf us 2018

\usetheme[]{metropolis}

@@

\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{array}
\usepackage{colortbl}
\tcbuselibrary{skins}

@@

\newcommand\tikzmark[1]{%
  \tikz[overlay,remember picture] \coordinate (#1);}

@@

    \ifx\inserttitle\@empty\else
    {{% \inserttitle is nonempty
      \raggedright%
      %\linespread{1.0}%
      \usebeamerfont{title}%
      \usebeamercolor[fg]{title}%
      %\vspace*{1.3em}
      \if@noSmallCapitals%
        \inserttitle%
      \else%
        \scshape{\color{black} \textbf{\begin{center}\inserttitle\end{center}}}%
      \fi%
      \vspace*{0.3em}
    }}
    \fi

@@

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 20-04-2018}%

@@

\title{NOSQL\\ BEST PRACTICES}
\subtitle{FOR POSTGRESQL}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

@@

@@

\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Introduction}

        \begin{itemize}[label={}]
            \item Less benchmarks
            \item More opinionated best practices
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Introduction}

        \begin{itemize}[label={}]
            \item Application developers
            \item DBAs
            \item Extension developers
        \end{itemize}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{Application developers}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{When jsonb?}
        \begin{itemize}
            \item <+->
        \end{itemize}

        \begin{itemize}[label={\MVRightarrow}]
            \item <+-> You have a distinct flexible model
            \item <+-> You need to work with data provided in document oriented format
            \item <+-> Workaround for technical issues (large number of tables or expensive alignment)
        \end{itemize}

    \end{center}
\end{frame}
\note{
    technical reasons - Because of some performance issues you want to keep
    number of relations as small as possible (so, you denormalize some data),
    or you're playing with alignment
}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{When not jsonb?}
        \begin{itemize}
            \item <+->
        \end{itemize}

        \begin{itemize}[label={\MVRightarrow}]
            \item <+-> Flexibility "just in case"
            \item <+-> Reluctance to create a migration
            \item <+-> Use jsonb column as a "garbage can"
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Jsonb -> Relation}

        \begin{columns}[T,onlytextwidth]
        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{document.jpg}
        \end{itemize}

        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{relation.png}
        \end{itemize}

        \end{columns}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{When to move from jsonb to relation?}
        \begin{itemize}
            \item <+->
        \end{itemize}

        \begin{itemize}[label={\MVRightarrow}]
            \item <+-> Queries rely significantly in information about\\
                internal structure of documents
            \item <+-> There are too many constraints for documents
            \item <+-> Some parts of document are used much more\\
                frequently than other
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_where.sql}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated conditions}

        \begin{itemize}[label={\MVRightarrow}]
            \item jsquery
            \item SQL/JSON
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated conditions}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_where_jsquery.sql}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated conditions}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_where_standard.sql}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Complicated select}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/complex_select.sql}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Jsonb -> Relation}

        \begin{columns}[T,onlytextwidth]
        \column{0.3\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=4cm,height=4cm]{document.jpg}
        \end{itemize}

        \column{0.3\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=4cm,height=4cm]{schema.jpg}
        \end{itemize}

        \column{0.3\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=4cm,height=4cm]{relation.png}
        \end{itemize}

        \end{columns}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Constraints}

        \begin{itemize}[label={\MVRightarrow}]
            \item Simple checks for value, type or size
            \item More convenient checks with jsquery
            \item Json schema
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Constraints}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/constraints.sql}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Relation -> Jsonb}

        \begin{columns}[T,onlytextwidth]
        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{relation.png}
        \end{itemize}

        \column{0.5\textwidth}
        \begin{itemize}[leftmargin=*]
            \item \includegraphics[width=6cm,height=5cm]{document.jpg}
        \end{itemize}

        \end{columns}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \inputminted[
            fontsize=\large,
        ]{sql}{sql/jsonb_agg.sql}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{Seamless interaction\\ between json and relation}
\fontsize{17pt}{18}\selectfont

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \inputminted[
        fontsize=\Large,
    ]{json}{sql/with_array_data.json}

    \end{center}
\end{frame}

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \begin{overprint}
    \onslide<1>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/with_array.sql}

    \onslide<2>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/with_array_highlight.sql}
    \end{overprint}

    \inputminted[
        fontsize=\large,
    ]{bash}{sql/with_array.sh}

    \end{center}
\end{frame}

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \inputminted[
        fontsize=\Large,
    ]{json}{sql/iterate_document_data.json}

    \end{center}
\end{frame}

\fontsize{17pt}{19}\selectfont
\begin{frame}
    \frametitle{}
    \begin{center}

    \begin{overprint}
    \onslide<1>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/iterate_document.sql}

    \onslide<2>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
        ]{sql}{sql/iterate_document_highlight.sql}
    \end{overprint}

    \inputminted[
        fontsize=\large,
    ]{bash}{sql/iterate_document.sh}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Multiple jsonb columns}

        \begin{itemize}[label={\MVRightarrow}]
            \item Keep at the end for readability
            \item tuple\_deform (PG11, JIT compilation)
        \end{itemize}

    \end{center}
\end{frame}
\note{
    with JIT compilation tuple deform can be faster up to 2 times
}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Multiple jsonb columns}

        \vspace{1cm}
        \onslide<1,2,3,4>
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
            \tikzmark{start}value & \tikzmark{right} value & value & value & value & value... \\\hline
        value & value & value & value & value & value... \\\hline
        \tikzmark{end}value & value & value & value & value & value...
        \end{tabular}
        \end{tcolorbox}

        \onslide<2,3,4>
        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm, color=white]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(1.5,1.3)$) -- node[] {} ($(\x1,\y2)+(12.0,1.3)$);
        \end{tikzpicture}

        \onslide<3,4>
        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm]
            let \p1=(start), \p2=(end) in ($(\x1,\y1)+(-1.2,0.2)$) -- node[] {} ($(\x1,\y2)+(-1.2,0.0)$);
        \end{tikzpicture}

        \onslide<4>
        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(9.3,0.8)$) rectangle ($(\x1,\y2)+(12.0,-2.1)$);
        \end{tikzpicture}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Multiple jsonb columns}

        \vspace{1cm}
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
        \tikzmark{start}value... & \tikzmark{right} value & value & value & value & value \\\hline
        value... & value & value & value & value & value \\\hline
        \tikzmark{end}value... & value & value & value & value & value
        \end{tabular}
        \end{tcolorbox}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm]
            let \p1=(start), \p2=(end) in ($(\x1,\y1)+(-1.2,0.2)$) -- node[] {} ($(\x1,\y2)+(-1.2,0.0)$);
        \end{tikzpicture}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm, color=white]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(1.5,1.3)$) -- node[] {} ($(\x1,\y2)+(12.0,1.3)$);
        \end{tikzpicture}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(-0.3,0.8)$) rectangle ($(\x1,\y2)+(2.1,-2.1)$);
        \end{tikzpicture}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Document slice: in the DB or in the app?}

        \begin{itemize}[label={\MVRightarrow}]
            \item Amount of data passed from DB to application
            \item Performance hit in some cases\\ (multiple detoasting)
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \begin{overprint}
    \onslide<1>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/detoast_overhead.sql}

    \onslide<2>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/detoast_overhead_ok.sql}

    \onslide<3>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/detoast_overhead_wrong.sql}
    \end{overprint}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{select.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \begin{itemize}[label={\MVRightarrow}]
            \item Plain Json
            \item Binary Jsonb
            \item Relation
        \end{itemize}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{Insert workload}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{json_vs_jsonb_insert.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{jsonb_vs_relation_insert.png}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{Read workload}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{json_vs_jsonb_read.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{jsonb_vs_relation_read.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Jsonb array vs regular array}

        \begin{itemize}[label={\MVRightarrow}]
            \item Store elements of different type?\\
                    Not really a "single model" idea.
            \item Syntax is less natural (this may change)
            \item Updates are slower
            \item Arrays are 1-based, Jsonb 0-based
        \end{itemize}

    \end{center}
\end{frame}
\note {
    arrays are copied too, where exactly jsonb slower?
}

\begin{frame}
    \frametitle{}
    \begin{center}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/array_vs_jsonb.sql}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Jsonb NULL != SQL NULL}

        \inputminted[
            fontsize=\Large,
            escapeinside=||
        ]{sql}{sql/jsonb_sql_null.sql}

        \inputminted[
            fontsize=\large,
        ]{bash}{sql/jsonb_sql_null.sh}

        \inputminted[
            fontsize=\Large,
            escapeinside=||
        ]{sql}{sql/jsonb_null.sql}

        \inputminted[
            fontsize=\large,
        ]{bash}{sql/jsonb_null.sh}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Some useful extensions}

        \begin{itemize}[label={\MVRightarrow}]
            \item jsquery
            \item postgres-json-schema
            \item is\_jsonb\_valid
            \item zson (custom compression methods WIP)
            \item jsonb\_explorer
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Types, please}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.7\textwidth,center]{fuzzy.jpg}

        \vspace{-2cm}
        \tiny{\href{https://kickass-peanut.deviantart.com/}{@kickass-peanut}}

    \end{center}
\end{frame}
\note {
    "Types, please"
}

\fontsize{13pt}{14}\selectfont
\section{DBAs}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Limitations}

        \begin{itemize}[label={}]
            \item Size 256 MB
            \item Depth - max\_stack\_depth
            \item Stack depth is different for create \& update
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{cat.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Indexing support}

        \begin{itemize}[label={\MVRightarrow}]
            \item GIN index (jsonb\_ops, jsonb\_path\_ops)
            \item Functional BTree index
            \item jsquery strategies for GIN
            \item Partial indexes WIP
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Place for ID}

        \begin{itemize}[label={\MVRightarrow}]
            \item Inside a document
            \item As as separate column
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.75\textwidth,center]{pg_id_place.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Place for ID}

        \begin{flushleft}
            PostgreSQL 11 have HOT updates for some expression indexes, which will
            eliminate this problem.
        \end{flushleft}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Statistics}

        \begin{itemize}[label={\MVRightarrow}]
            \item There is no proper selectivity estimation for jsonb
            \item Optimizer can give wrong estimations for GIN and complex queries
            \item Functional indexes
        \end{itemize}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{How much to write?}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Jsonb vs Json}

        \includegraphics[width=0.7\textwidth,center]{jsonb_header.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.8\textwidth,center]{wal.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{How much to write?}

        \begin{itemize}[label={\MVRightarrow}]
            \item Every update leads to update of an entire document (but it's ok)
            \item WAL can have a full document or just a diff
            \item Old and new tuples fit into the same page - diff
            \item If logical decoding is enabled - full
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{How much to write?}

    \vspace{0.5cm}
    \onslide<1,2,3,4,5>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {};
        \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {};
    \end{tikzpicture}

    \vspace{-0.5cm}
    \onslide<2,3,4,5>
    \begin{tikzpicture}
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (6,-0.5);
        \draw[<-, line width=1mm, dashed] (8,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \vspace{0.5cm}
    \onslide<3>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
    \end{tikzpicture}

    \vspace{-1.28cm}
    \onslide<4>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (2,-0.5);
        \draw[<-, line width=1mm, dashed] (10,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \vspace{-1.8cm}
    \onslide<5>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm, fill=red!30] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (2,-0.5);
        \draw[<-, line width=1mm, dashed] (10,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Huge documents}

        \begin{itemize}[label={\MVRightarrow}]
            \item TOAST has significant overhead (assemble, locks)
            \item Other than that ~ linear degradation
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \includegraphics[width=0.7\textwidth,center]{document_size.png}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Alignment}

    \begin{itemize}[label={}]
        \item Variable-length portion is aligned to a 4-byte
        \item \inputminted[fontsize=\Large]{sql}{sql/insert_align1.sql}
        \item \begin{figure}
            \includegraphics[width=0.58\textwidth,left]{align_short.png}
        \end{figure}

        \item \inputminted[fontsize=\Large]{sql}{sql/insert_align2.sql}
        \item \begin{figure}
            \includegraphics[width=0.75\textwidth,left]{align_long.png}
        \end{figure}

    \end{itemize}

    \end{center}
\end{frame}

\fontsize{13pt}{14}\selectfont
\section{Extensions}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Why write an extension?}

        \vspace{1cm}
        \begin{itemize}[label={\MVRightarrow}]
            \item Implement some convenient functionality\\ (e.g. jsonb intersection)
            \item Create function optimized for your domain model
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Why write an extension?}

        \vspace{1.0cm}

        \only<1>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm, color=white] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
            \end{tikzpicture}
        }

        \only<2>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
            \end{tikzpicture}
        }

        \only<3>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
                \draw[->, line width=0.75mm] (7,-0.5) to [controls=+(-90:1) and +(-90:1)]  (5,-0.5);
            \end{tikzpicture}
        }

        \only<4>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
                \draw[->, line width=0.75mm] (7,-0.5) to [controls=+(-90:1) and +(-90:1)]  (5,-0.5);
                \draw[->, line width=0.75mm] (5,-0.5) to [controls=+(-90:1) and +(-90:1)]  (3,-0.5);
            \end{tikzpicture}
        }

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}

        \begin{itemize}[label={\MVRightarrow}]
            \item Raw Jsonb container when search for an element
            \item Iterate through JsonbValue when update
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Reuse infrastructure}

        \begin{itemize}[label={\MVRightarrow}]
            \item findJsonbValueFromContainer
            \item JsonbIterator
            \item addToParseState
            \item worker functions
        \end{itemize}

    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Random tips}

        \begin{itemize}[label={\MVRightarrow}]
            \item Clone iterator
            \item String are not null-terminated
        \end{itemize}

    \end{center}
\end{frame}

@@

      \usebeamerfont{subtitle}%
      \fontsize{13pt}{14}\selectfont
      \usebeamercolor[fg]{subtitle}%
        \begin{itemize}[label={}]
            \item {\color{black} \github\ github.com/erthalion}
            \item {\color{black} \twitter\ @erthalion}
            \item {\color{black}\email\ dmitrii.dolgov at zalando dot de}
            \item {\color{black}\email\ 9erthalion6 at gmail dot com}
        \end{itemize}
      \vspace*{2.5em}%

>>>>

\usetheme[]{m}

@@

@@

@@

    \ifx\inserttitle\@empty\else
    {{% \inserttitle is nonempty
      \raggedright%
      %\linespread{1.0}%
      \usebeamerfont{title}%
      \usebeamercolor[fg]{title}%
      %\vspace*{1.3em}
      \if@noSmallCapitals%
        \inserttitle%
      \else%
        \scshape{\color{black} \textbf{\begin{center}NOSQL FOR\\POSTGRESQL\end{center}}}%
      \fi%
      \vspace*{0.3em}
    }}
    \fi

@@

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 12-05-2017}%

@@

\title{NOSQL INSIDE SQL}
\subtitle{BEST PRACTICES}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

@@

\fontsize{17pt}{19}\selectfont
\section{}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
    \end{center}
\end{frame}

@@

      \usebeamerfont{subtitle}%
      \fontsize{13pt}{14}\selectfont
      \usebeamercolor[fg]{subtitle}%
        \begin{itemize}[label={}]
            \item {\color{black} \github\ github.com/erthalion}
            \item {\color{black} \twitter\ @erthalion}
            \item {\color{black}\email\ 9erthalion6 at gmail dot com}
        \end{itemize}
      \vspace*{2.5em}%
